\textbf{AprilTrack: A Particle-Filter based AprilTag Tracker}

### 2017-01-30 paper/paper.tex
Trying to get bold stuff fixed

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}

\usepackage{cite}
\usepackage{graphicx}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{pgfplots}

@@

\renewcommand{\vec}[1]{\boldsymbol{#1}}

@@

@@

As the particles are drawn from the proposal distribution $q(\vec{x})$, the sample weight $w^i$ must take into account any discrepancy between $p(\vec{x})$ and $q(\vec{x})$ so that $w^i_t \propto p(\vec{x}^i_{1:t}|\vec{z}_{1:t})/q(\vec{x}^i_{1:t}|\vec{z}_{1:t})$.

@@

The AprilTrack algorithm was primarily evluated on a manually-labeled single-tag sequence with a moving tag. The algorithm was also run on an ego-motion multi-tag sequence which will be qualitatively discussed.
\footnote{Videos of the sequences and the tracker's performance are available online at https://www.youtube.com/watch?v=kV8z3st9rlk and https://www.youtube.com/watch?v= }

@@

\bibliographystyle{unsrt}
\bibliography{paper_bib}{}

>>>>

\documentclass[letterpaper, 10 pt]{IEEEconf}

%\makeatletter
%\let\NAT@parse\undefined
%\makeatother

\usepackage{graphicx}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{pgfplots}

%\usepackage{natbib}
%\usepackage{hyperref}
%\usepackage{caption}
%\usepackage{url}

@@

\renewcommand{\vec}[1]{#1}

@@

%\newcommand{\citep}[1]{\cite{#1}}
%\newcommand{\url}[1]{#1}

@@

As the particles are drawn from the proposal distribution $q(\vec{x})$, the sample weight $w^i$ must take into account any discrepancy between $p(\vec{x})$ and $q(\vec{x})$ so that $w^i_t \propto p(\vec{x}^i_{1:t}|\vec{z}_{1:t})/q(\vec{x}^i_{1:t}|\vec{z}_{1:t})$. From this observation we note that therefore:

\begin{equation*}
	w^i_{t} \propto \frac{p(\vec{x}^i_{0:t}|\vec{z}_{1:t})}{q(\vec{x}^i_{0:t}|\vec{z}_{1:t}) }
\end{equation*}

@@

The AprilTrack algorithm was primarily evluated on a manually-labeled single-tag sequence with a moving tag. The algorithm was also run on an ego-motion multi-tag sequence which will be qualitatively discussed.
\footnote{Videos of the sequences and the tracker's performance are available online at https://www.youtube.com/watch?v=kV8z3st9rlk and https://www.youtube.com/watch?v=F5cFTLBlJ1s }

@@

\bibliographystyle{abbrv}
\bibliography{paper_bib}{}
